### 2020-08-12 LaTeX/sections/paper.tex
Updates on the text

\item \textbf{Speed.}

\item \textbf{Front-running and Censorship.}

\item \textbf{Enforcing Time.}

@@

% = = = = = = = = = = = =Clearing Mappings = = = = = = = = = = = = =  %
\section{Clearing Mappings}

@@

\item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens. Note that using this solution, traders can only claim their funds (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is in state \texttt{Closed}.

\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the CallMarket smart contract. This counter is incremented at the end of the matching process. So instead of clearing the mapping, we only use another portion of it every time the market opens.

\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be killed at the end of the matching process.

\item \textbf{Storing the Mapping keys in additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that. This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process. Not that this is a gas-costly design pattern as we would need to maintain a secondary data structure.

@@

%= = = = = =Mapping with Keys Stored in Heap = = = = = = =%

@@

%= = = = = =Linkedlist = = = = = = =%

\subsection {Linkedlist}
Every time a trade happens, we use the \texttt{self-destruct} operation to remove the nodes (\ie smart contracts) containing the best bid and ask orders from the Ethereum blockchain. When a node is deleted, it transfers its funds (if any) to the payable address of the CallMarket contract that has been previously passed to it as a constructor argument. Also, removing a smart contract from the Ethereum blockchain refunds 24000 gas to the caller.

%= = = = = =Linkedlist with Mapping = = = = = = =%

\subsection {Linkedlist with Mapping}
Every time a trade happens when the \texttt{Match()} function is executed, the best bid and ask orders need to be removed from the data structures. We could do this in two different ways; (i) update the head and tail pointers of the linkedlist and/or (ii) removing the mapping elements that contain the best bid and ask orders from storage completely as well as updating the pointers of the linkedlist. \par

For the same reason we mentioned in~\ref{sec:mapping_heap}, we clear the best bid and ask order structs from the mapping every time a trade happens as well as updating the pointers.

@@

% We use one-shot market for the sake of our performance tests on different datastructures. and once we have all the numbers we can think about iterated market.

@@

%%%%% Mahsa: Add whatever was discussed in the meeting %%%%%

@@

%Jeremy: Miner could close the market as they get paid and the amount could be more than running the function. 
\item \textbf {Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}. In our design, when the trade occurs between the the highest bid (the highest amount a buyer is willing to pay for an asset) and lowest ask (the lowest amount a seller is willing to accept for an asset) orders, the bid-ask spread is paid to the miner. In addition to this, a miner could close the market and get refunded. The refund amount could be potentially higher than the bid-ask spread which provides enough economic incentives for the miner to execute the \texttt{Close()} function.

% = = = = = = = = = =Processing Orders in Groups= = = = = = = = = = = = = = = %
% Mahsa: Title is good or needs to be changed?

>>>>

\begin{itemize}
%---------+++++++++++++++++++-----------------
\item \textbf{Speed.}

%---------+++++++++++++++++++-----------------
\item \textbf{Front-running and Censorship.}

%---------+++++++++++++++++++-----------------
\item \textbf{Enforcing Time.}

%---------+++++++++++++++++++-----------------

@@

% = = = = = = = = = = = =Clearing Mappings = = = = = = = = = = = = =  %

\section{Clearing Mappings}

@@

%---------+++++++++++++++++++-----------------
\item \textbf{Creating a New Mapping Every Time the Market Opens.} Instead of clearing the \texttt{UnavailableBalance} of traders at the end of a matching process, we could create a new mapping every time the market opens. Note that using this solution, traders can only claim their funds (using the \texttt{ClaimEther()} and/or \texttt{ClaimToken} methods) only when the market is in state \texttt{Closed}.

%---------+++++++++++++++++++-----------------
\item \textbf{Creating Custom Keys for the Mapping.} We can create custom keys for the mapping by defining a counter as a global variable inside the CallMarket smart contract. This counter is incremented at the end of the matching process. So instead of clearing the mapping, we only use another portion of it every time the market opens.

%---------+++++++++++++++++++-----------------
\item \textbf{Storing the Mapping in a Data-Contract.} Another design proposal is to create a smart contract every time the market opens, this data contract only stores the \texttt{UnavailableBalance} mapping and will be killed at the end of the matching process.

%---------+++++++++++++++++++-----------------
\item \textbf{Storing the Mapping keys in an additional Array.} Another common pattern is to create an additional array on top of the mapping and iterate over that. This array (\eg address[]) stores the traders' addresses and enables us to iterate over the mapping and delete individual keys and what they map to at the end of the matching process. Not that this is a gas-costly design pattern as we would need to maintain a secondary data structure.

%---------+++++++++++++++++++-----------------

@@

%---------+++++++++++++++++++-----------------

@@

%---------+++++++++++++++++++-----------------
\subsection {Linkedlist}
Every time a trade happens, we use the \texttt{self-destruct} operation to remove the nodes (\ie smart contracts) containing the best bid and ask orders from the Ethereum blockchain. When a node is deleted, it transfers its funds (if any) to the payable address of the CallMarket contract that has been previously passed to it as a constructor argument. Also, removing a smart contract from the Ethereum blockchain refunds 24000 gas to the caller.

%---------+++++++++++++++++++-----------------
\subsection {Linkedlist with Mapping}
Every time a trade happens when the \texttt{Match()} function is executed, the best bid and ask orders need to be removed from the data structures. We could do this in two different ways; (i) update the head and tail pointers of the linkedlist and/or (ii) removing the mapping elements that contain the best bid and ask orders from storage completely as well as updating the pointers of the linkedlist. \par
For the same reason we mentioned in~\ref{sec:mapping_heap}, we clear the best bid and ask order structs from the mapping every time a trade happens as well as updating the pointers.

@@

% We use one-shot market for the sake of our performance tests on different data structures. and once we have all the numbers we can think about iterated market.

@@

@@

\item \textbf {Miners Close and Reopen the Market.} The difference between the best bid and ask prices is called the \textit{bid-ask spread}. In our design, when the trade occurs between the the highest bid (the highest amount a buyer is willing to pay for an asset) and lowest ask (the lowest amount a seller is willing to accept for an asset) orders, the bid-ask spread is paid to the miner. There are possibilities that (i) no trade occurs or (ii) the bid-ask spread is zero (\ie the best bid and best ask prices are identical). So there is enough economic incentive for the the miner to execute the \texttt{CloseMarket()} function and get refunded as the refund amount could be potentially higher than the bid-ask spread.

% = = = = = = = = = =Processing Orders in Groups= = = = = = = = = = = = = = = %
